On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-15 MS.tex
Figure3,4, A3, A4, A5 : fix label, alignment etc Figure A4: delete pannel 2 (was redundant with Fig3) remake.yml: shut off figureA4.1 MS: modification caption of Fig 1, 2, 3 and A4.

% Todo:
% Ditch abbrvos for SLA, wood density, Hmax?
% Fix plots
%   -- labels causing plot size to change, e.g. Fig 3d
%   -- only one y label for multi-panel plots
%   -- sample sizes skewiff relative to plots if Figure 4
%   -- major revision of code -- > lots of repetition, hard to follow
%   -- Figure 2: add * against traits used in meta-analysis

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications (coloured lines), compared to standardised thresholds used in the analysis (black lines). Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. The solid vertical lines indicate the thresholds used to classify plants in one of three stages. Studies mark with a ``*'' were those where stage was changed or assigned, compared to the original publication. }
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by size and trait. Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means adding a stage effect to the model significantly improved model fit. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits, measured by stage (a-e
) and by stage and growth type (f-j). a and f) Specific leaf area (SLA), b and g) Wood density (WD), c and h) Asymptotic maximum height (Hmax), d and i) Seed mass (Seedmass) and e and j) Rate of CO2 assimilation (Aarea). On figures f to j, relative (RGR) and absolute (AGR) growth rates are set apart. The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

>>>>

% Todo:
% Ditch abbrvos for SLA, wood density, Hmax?
% Fix plots
%   -- labels causing plot size to change, e.g. Fig 3d
%   -- only one y label for multi-panel plots
%   -- major revision of code -- > lots of repetition, hard to follow
%   -- Figure 2: add * against traits used in meta-analysis

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-anlyses. Studies mark with a ''*'' were those where stage was changed or assigned, compared to the original publication. }
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait. Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across >10 species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means adding a stage effect to the model significantly improved model fit. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}
